manuscript_outline

### 2025-07-03 docs/manuscript/paper.Rmd
copy edits
added more refs to table2

| Class        | Order         | Genera         | Species            | Study                                     |
|:--------------|:--------------|:--------------|:--------------|:--------------|
| Amphibia     | Anura         | *Lithobates*   | *L. sylvaticus*    | @moore1939                                |
|              |               |                | *L. pipiens*       |                                           |
|              |               |                | *L. clamitans*     |                                           |
|              |               |                | *L. palustris*     |                                           |
|              |               | *Ascaphus*     | *A. truei*         | @brown1975                                |
|              | Urodela       | *Ambystoma*    | *A. gracile*       | @brown1976                                |
| Reptilia     | Squamata      | *Sceloporus*   | *S. undulatus*     | @angilletta2000                           |
|              |               | *Podarcis*     | *P. mural*is       | @vandamme1992                             |
|              | Testudines    | *Mauremys*     | M. reevesii        | @du2007                                   |
|              |               |                | 181 species        | 141 studies in @while2018                 |
| Insecta      | Plecoptera    | *Nemurella*    | *N. pictetii*      | @brittain1978, @elliott1984               |
|              |               | *Capnia*       | *C. atra*          | @brittain1984                             |
|              |               | *Capnia*       | *C. bifrons*       | @elliott1986                              |
|              |               | *Mesocapnia*   | *M. oenone*        | @brittain1984                             |
|              |               | *Taeniopteryx* | *T. nebulosa*      | @brittain1977                             |
|              | Coleoptera    | *Colaphellus*  | *C. bowringi*      | @tang2017                                 |
|              |               |                | 18 species         | Developmental equations in @pritchard1987 |
| Malacostraca | Decapoda      | *Pontastacus*  | *P. leptodactylus* | @aydin2004                                |
| Copepoda     | Calanoida     | 13 genera      |                    | <https://doi.org/10.1086/662174>          |
|              | Cyclopoida    | 3 genera       |                    | <https://doi.org/10.1086/662174>          |
|              | Harpacticoida | 2 genera       |                    | <https://doi.org/10.1086/662174>          |

>>>>

| Class        | Order         | Genera          | Species            | Study                                                                                                   |
|:--------------|:--------------|:--------------|:--------------|:--------------|
| Amphibia     | Anura         | *Lithobates*    | *L. sylvaticus*    | @moore1939                                                                                              |
|              |               |                 | *L. pipiens*       |                                                                                                         |
|              |               |                 | *L. clamitans*     |                                                                                                         |
|              |               |                 | *L. palustris*     |                                                                                                         |
|              |               | *Ascaphus*      | *A. truei*         | @brown1975                                                                                              |
|              | Urodela       | *Ambystoma*     | *A. gracile*       | @brown1976                                                                                              |
| Reptilia     | Squamata      | *Sceloporus*    | *S. undulatus*     | @angilletta2000                                                                                         |
|              |               | *Podarcis*      | *P. mural*is       | @vandamme1992                                                                                           |
|              | Testudines    | *Mauremys*      | M. reevesii        | @du2007                                                                                                 |
|              |               |                 | 181 species        | 141 studies in @while2018                                                                               |
| Insecta      | Plecoptera    | *Nemurella*     | *N. pictetii*      | @brittain1978, @elliott1984                                                                             |
|              |               | *Capnia*        | *C. atra*          | @brittain1984                                                                                           |
|              |               | *Capnia*        | *C. bifrons*       | @elliott1986                                                                                            |
|              |               | *Mesocapnia*    | *M. oenone*        | @brittain1984                                                                                           |
|              |               | *Taeniopteryx*  | *T. nebulosa*      | @brittain1977                                                                                           |
|              | Coleoptera    | *Colaphellus*   | *C. bowringi*      | @tang2017                                                                                               |
|              |               |                 | 18 species         | Developmental equations in @pritchard1987                                                               |
|              |               | *Dendroctonus*  | *D. ponderosae*    | Régnière et al. (2012) [10.1016/j.jinsphys.2012.01.010](https://doi.org/10.1016/j.jinsphys.2012.01.010) |
|              | Lepidoptera   | *Choristoneura* | *C. fumiferana*    | Régnière et al. (2012) [10.1016/j.jinsphys.2012.01.010](https://doi.org/10.1016/j.jinsphys.2012.01.010) |
|              |               | *Zeiraphera*    | *Z. canadensis*    | Régnière et al. (2012) [10.1016/j.jinsphys.2012.01.010](https://doi.org/10.1016/j.jinsphys.2012.01.010) |
|              | Diptera       | *Bactrocera*    | *B. cucurbitae*    | Régnière et al. (2012) [10.1016/j.jinsphys.2012.01.010](https://doi.org/10.1016/j.jinsphys.2012.01.010) |
| Malacostraca | Decapoda      | *Pontastacus*   | *P. leptodactylus* | @aydin2004                                                                                              |
| Copepoda     | Calanoida     | 13 genera       |                    | Forster et al. (2011) <https://doi.org/10.1086/662174>                                                  |
|              | Cyclopoida    | 3 genera        |                    | Forster et al. (2011) <https://doi.org/10.1086/662174>                                                  |
|              | Harpacticoida | 2 genera        |                    | Forster et al. (2011) <https://doi.org/10.1086/662174>                                                  |
| Cephalopoda  | Octopoda      | *Octopus*       | 2 species          | Márquez et al. (2021) [**https://doi.org/10.1111/raq.12495**](https://doi.org/10.1111/raq.12495)        |
|              | Myopsida      | *Loligo*        | 2 species          | Márquez et al. (2021) [**https://doi.org/10.1111/raq.12495**](https://doi.org/10.1111/raq.12495)        |
|              | Oegopsida     | 3 genera        |                    | Márquez et al. (2021) [**https://doi.org/10.1111/raq.12495**](https://doi.org/10.1111/raq.12495)        |
